Adaptative neighbouring methods applied to telephonic base stations

### 2024-08-23 article.tex
related works

    This article aims at enhance the precision of these methods . It also aims at comparing the efficiency of different approaches.

@@

\section{Related works\label{sec:rel_works}}
    \noindent When looking for neighbours, the first method that comes in mind is $k$-NN.

>>>>

    This article aims at enhance the precision of these methods. It also aims at comparing the efficiency of different approaches.

@@

\section{Related works\label{sec:rel_works}}
    \noindent When looking for neighbours, the first method that comes in mind is $k$-NN \cite{10201211}.

    However, this method is not the most adapted to our specific problem. Consequently, more adapted methods can be found.

    For example, the second method that is used to resolve such a problem is the Delaunay triangulation \cite{delaunay_neighbor} but this is still not perfect. For instance, on the border of the set of points some neighbouring connexion does not reflect the reality of physics. As a consequence, a method to filtrate those connexions needs to be implemented.

    So, to solve this new problem, there is existing methods that can be sufficient \cite{art_del_paq, patent_neighs}, i.e. applying the same criteria for each BS.

    Taking those existing methods into account, we realised that they are still not sufficient. Then, here is the major improvement of our work: take account of differences in BSs' density.
